Authors Response to Reviewer's Comments

### 2023-10-31 manuscript/review/authorsResponse.qmd
comment 3

The objective of running the t-tests was to allow us to discuss differences between mean values per site between models, and observations and simulations between the 7 and 10 cm diameter thresholds. The t-test, as employed in our study, is not intended to serve as \'proof\' of our findings, and we have carefully avoided an over-interpretation of their outcomes. Rather, they serve as a practical tool for handling the extensive number of comparisons in our study. To clarify this, we have included a statement in the manuscript, cf. L\[336-337\].

Following the reviewer\'s comment, we have included a correction for multiple tests, although we are aware that all corrections have pros and cons. We used the Bonferroni correction to make sure that the actual Type I error probability for the combined H0 is smaller than or equal to the nominal test level.

We have also looked into the alternative approaches suggested by the reviewer. We cannot do a paired t-test as for paired samples it is necessary to have the same number of subjects in both groups (observed and simulated), which is not the case here, as for example some models did not simulate all the sites. Yet, we tested the possibility of creating a GLME using as random effect the site and as explanatory variables all the features that we were interested in (model complexity, feedback, model type and scale), as suggested by the reviewer. However, this approach does not provide the comparison of observed vs. simulated data that we are interested in. Following the reviewer\'s comments, we conducted further tests to see if we could better explain differences between observed and simulated values using other approaches. We tested a mixed model to account for the randomness induced by to site (plot) differences. For example, a GLME with recruitment values as the response variable and models as the explanatory variable, with observed data as the reference (with a Poisson distribution because we are dealing with count data). This worked well, and the patterns were the same as in the t-test (except for the model 4C). We also considered pursuing the same approach with the Shannon index and the differences in mortality, but in this case we think it is more relevant to understand the mean differences across sites, and therefore a t-test is more suitable. We furthermore tested a linear mixed model to assess differences between the 7 and 10 cm thresholds regarding the Shannon index, by creating a new parameter where the explanatory variable was a combination of the model and the diameter threshold. We then ran pairwise multiple comparisons to determine which means are different. Also here, the patterns were quite similar to the ones resulting from the t-test except for two landscape-level models (TreeMig and Landis-II) that were significant in this test, contrary to the t-test.

>>>>

The objective of running the t-tests was to allow us to discuss differences between mean values per site between models, and observations and simulations between the 7 and 10 cm diameter thresholds. The t-test, as employed in our study, is not intended to serve as 'proof' of our findings, and we have carefully avoided an over-interpretation of their outcomes. Rather, they serve as a practical tool for handling the extensive number of comparisons in our study. To clarify this, we have included a statement in the manuscript, cf. L\[336-337\].

Following the reviewer's comment, we have included a correction for multiple tests, although we are aware that all corrections have pros and cons. We used the Bonferroni correction to make sure that the actual Type I error probability for the combined H0 is smaller than or equal to the nominal test level.

We have also looked into the alternative approaches suggested by the reviewer. We cannot do a paired t-test as for paired samples it is necessary to have the same number of subjects in both groups (observed and simulated), which is not the case here, as for example some models did not simulate all the sites. Yet, we tested the possibility of creating a GLME using as random effect the site and as explanatory variables all the features that we were interested in (model complexity, feedback, model type and scale), as suggested by the reviewer. However, this approach does not provide the comparison of observed vs. simulated data that we are interested in. Following the reviewer's comments, we conducted further tests to see if we could better explain differences between observed and simulated values using other approaches. We tested a mixed model to account for the randomness induced by to site (plot) differences. For example, a GLME with recruitment values as the response variable and models as the explanatory variable, with observed data as the reference (with a Poisson distribution because we are dealing with count data). This worked well, and the patterns were the same as in the t-test (except for the model 4C). We also considered pursuing the same approach with the Shannon index and the differences in mortality, but in this case we think it is more relevant to understand the mean differences across sites, and therefore a t-test is more suitable. We furthermore tested a linear mixed model to assess differences between the 7 and 10 cm thresholds regarding the Shannon index, by creating a new parameter where the explanatory variable was a combination of the model and the diameter threshold. We then ran pairwise multiple comparisons to determine which means are different. Also here, the patterns were quite similar to the ones resulting from the t-test except for two landscape-level models (TreeMig and Landis-II) that were significant in this test, contrary to the t-test.
